**Preprinting Microbiology**

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Address confusion in Issue #25
Made it more clear that the section refers to the current manuscript. I
also populated the numbers as of March 13, 2017. Closes #25.

***Preprints from an author's perspective.*** Posting research as a preprint gives an author great control over when their work is made public. Under the traditional peer-review model, an author may need to submit and revise their work multiple times to several journals over a long period before it is finally published. In contrast, an author can post the preprint at the start of the process for others to consume and comment on as it works its way through the editorial process. A first example illustrates the utility of preprints for improving access to research and the quality of its reporting. In 2014, my research group posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform [@Schloss2015]. At the same time, they submitted the manuscript for review at *PeerJ*. While the manuscript was under review, they received feedback from an academic scientist and from scientists at Pacific Biosciences that the impact of the results could be enhanced by using a recently released version of the sequencing chemistry. Instead of ignoring this feedback and resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to *PeerJ* that incorporated the original reviews as well as the feedback we received from the academic scientist and Pacific Biosciences. It was eventually published by *PeerJ* [@Schloss2016a; @Schloss2016b]. Since 2015, we have continued to post manuscripts as preprints at the same time as we have submitted manuscripts. Although the feedback to other manuscripts has not been as helpful as our initial experience, we were able to sidestep lengthy review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b]. As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **February XX, 2017**. I then solicited feedback on the manuscript using social media. Two weeks later, I incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*. During that time, the abstract was read **XXXX** times and the PDF was accessed **XXXX** times. This process engaged **XXXX** commenters on *bioRxiv*, **XXXX** people on Twitter, **XXXX** on Facebook, and **XXXX** via email. I received useful feedback from **XXX** people. Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had I foregone the posting of a preprint. Although there are concerns regarding the quality of the science posted to a preprint server, I contend that responsible use of preprints as a part of the scientific process can significantly enhance the science.

***Preprints from a publisher's perspective.*** A lingering question is what role traditional journals will have in disseminating research if there is broad adoption of preprints. Edited peer-reviewed journals offer and will continue to offer significant added value to a publication. A scholarly publishing ecosystem in which preprints coexist with journals will allow authors to gain value from the immediate communication of their work associated with preprints and also benefit from the peer-reviewed, professionally edited publication that publishers can provide.
The professional copyediting, layout, and publicity that these publishers offer are also unique features of traditional journals. An alternative perspective is that preprints will eventually replace traditional journals. Certainly, this is a radical perspective, but it does serve to motivate publishers to capture the innovation opportunities offered by preprints. By adopting preprint-friendly policies, journals can create an attractive environment for authors. As discussed above, a growing number of journals have created mechanisms for authors to directly submit preprints to their journals. An example is offered by the ASM, which earlier this year launched a new venture from *mSphere*. mSphereDirect is a publication track of the journal that capitalizes on the opportunity offered to couple preprints with rigorous peer-review. mSphereDirect. actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016]. ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles (Stefano Bertuzzi, personal communication). In addition to integrating preprints into the traditional editorial process, several professional societies have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016]. These are policies that empower authors and make specific journals more attractive. Other practices have great potential to improve the reputation of journals. As measured above, preprints are able to garner attention on par with papers published in highly selective microbiology journals. Thus, it is in a journal's best interest to recruit these preprints to their journals. Several journals including *PLOS Genetics* and *Genome Biology* have publicly stated that they scout preprints for this purpose [@Vence2017; @Barsh2016]. Preprints can also be viewed as a lost opportunity to journals. A preprint that garners significant attention may be ignored when it is finally published, brining little additional attention to the journal. Going forward, it will be interesting to see the innovative approaches that publishers develop so that they can benefit by incorporating preprints into their process and whether publishers' influence is reduced by the widespread adoption of preprints.

>>>>

***Preprints from an author's perspective.*** Posting research as a preprint gives an author great control over when their work is made public. Under the traditional peer-review model, an author may need to submit and revise their work multiple times to several journals over a long period before it is finally published. In contrast, an author can post the preprint at the start of the process for others to consume and comment on as it works its way through the editorial process. A first example illustrates the utility of preprints for improving access to research and the quality of its reporting. In 2014, my research group posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform [@Schloss2015]. At the same time, they submitted the manuscript for review at *PeerJ*. While the manuscript was under review, they received feedback from an academic scientist and from scientists at Pacific Biosciences that the impact of the results could be enhanced by using a recently released version of the sequencing chemistry. Instead of ignoring this feedback and resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to *PeerJ* that incorporated the original reviews as well as the feedback we received from the academic scientist and Pacific Biosciences. It was eventually published by *PeerJ* [@Schloss2016a; @Schloss2016b]. Since 2015, we have continued to post manuscripts as preprints at the same time as we have submitted manuscripts. Although the feedback to other manuscripts has not been as helpful as our initial experience, we were able to sidestep lengthy review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b]. As a second example, a preprint of the current manuscript was posted to *bioRxiv* on February 22, 2017. I then solicited feedback on the manuscript using social media. On March **13**, 2017 I incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*. During that time, the abstract was accessed **189** times and the PDF was accessed **107** times. This process engaged **3** commenters on *bioRxiv*, **61** people on Twitter, **2** people on the manuscript's GitHub repository, **1** person on a blog, and **2** via email. Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had I foregone the posting of a preprint. Furthermore, the preprint version of this manuscript had an Attention Score of **44**, which placed it in the top **5%** of all research scored by Altmetric. Although there are concerns regarding the quality of the science posted to a preprint server, I contend that responsible use of preprints as a part of the scientific process can significantly enhance the science.

***Preprints from a publisher's perspective.*** A lingering question is what role traditional journals will have in disseminating research if there is broad adoption of preprints. Edited peer-reviewed journals offer and will continue to offer significant added value to a publication. A scholarly publishing ecosystem in which preprints coexist with journals will allow authors to gain value from the immediate communication of their work associated with preprints and also benefit from the peer-reviewed, professionally edited publication that publishers can provide.

The professional copyediting, layout, and publicity that these publishers offer are also unique features of traditional journals. An alternative perspective is that preprints will eventually replace traditional journals. Certainly, this is a radical perspective, but it does serve to motivate publishers to capture the innovation opportunities offered by preprints. By adopting preprint-friendly policies, journals can create an attractive environment for authors. As discussed above, a growing number of journals have created mechanisms for authors to directly submit preprints to their journals. An example is offered by the ASM, which earlier this year launched a new venture from *mSphere*. mSphereDirect is a publication track of the journal that capitalizes on the opportunity offered to couple preprints with rigorous peer-review. mSphereDirect. actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016]. ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles (Stefano Bertuzzi, personal communication). In addition to integrating preprints into the traditional editorial process, several professional societies have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016]. These are policies that empower authors and make specific journals more attractive. Other practices have great potential to improve the reputation of journals. As measured above, preprints are able to garner attention on par with papers published in highly selective microbiology journals. Thus, it is in a journal's best interest to recruit these preprints to their journals. Several journals including *PLOS Genetics* and *Genome Biology* have publicly stated that they scout preprints for this purpose [@Vence2017; @Barsh2016]. Preprints can also be viewed as a lost opportunity to journals. A preprint that garners significant attention may be ignored when it is finally published, brining little additional attention to the journal. Going forward, it will be interesting to see the innovative approaches that publishers develop so that they can benefit by incorporating preprints into their process and whether publishers' influence is reduced by the widespread adoption of preprints.
